Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
some fixes

\subsection{Combineing \sfl{} and \cs{}}
\label{sec:comb}

@@

\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
\Rui{This is too rought. I would not talk about lithium right away.}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code . Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{|l|ccc|cccc|c|}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{3}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

		            & \% $k = 5$ & \% $k = 10$  & $\Delta$ & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%  &  0\%   & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 7.7\%  & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22.2 \%  & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 7.9\%   & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Sof{@todo: Add absolute numbers for SFL}\Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\subsection{Threats to validity}
%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community \Rui{cite d4j}.

@@

Program Slicing is an old technique with several applications in PL
and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
implemented in different ways. Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
context, failing tests exist. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and avoiding data and control omission
errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
cases where tests fail because some part of the code was not executed
when it should. Dynamic fault localization techniques cannot hope to
soundly report bugs in those cases. The issue is that incorporating
static information to capture those cases can result in unacceptably
large slices, which defeats the purpose of reducing the fault search
space. It is worth noting that, conceptually, the \comb{} combination
can be used with any form of dynamic slicing. We chose an
implementation of Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.

@@

Spectrum-based fault localization (\sfl) is amongst the most common statistical
fault localization technique that takes as input a test suite including at least
one failing test and reports on output a ranked list of components likely to be
in fault ~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.

\subsection{\comb{}}
\Rui{\comb{} ??}

>>>>

\subsection{Combining \sfl{} and \cs{}}
\label{sec:comb}

@@

\Rui{This is too rought. I would not talk about lithium right away.}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code . Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

\begin{table*}[h]
	\centering
	  \begin{tabular}{l|cc|cccc|c}
		\toprule
		\multirow{2}{*}{Project}            & \multicolumn{2}{c|}{SFL}  & \multicolumn{4}{c|}{\combpar{k}} & \multirow{2}{*}{\# Faults} \\

		            & \% $k = 5$ & \% $k = 10$  & \# $k = 5$ & \% $k = 5$ & \# $k = 10$ & \% $k = 10$ &  \\
		\midrule
		 \lang{}            & 84.1\%  & 84.1\%    & 63 & 100\% & 61 & 96.8\% & 63      \\
		% \cmath{}           & 82.08 \%  & 85.85 \% & 3.77 \%     \\   %\comments{& 177   &  -}\\
		% \closure{}         & 62.41 \%  & 72.18 \%  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 84.6\%  & 92.3\% & 20 & 76.9\% & 22 & 84.6\% & 26    \\  %\comments{& 92    &  -}\\
		\jtime{}           & 77.8 \%  & 100.0 \% & 22 & 81.5\% & 23 & 85.2\% & 27     \\   %\comments{& 76    &  -}\\
		 \mockito{}         & 63.2\%  & 71.1\% & 27 & 71.1\% & 30 & 79.0\% & 38 \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the buggy-lines is in the SFL and \combpar{k} report \Sof{@todo: Add absolute numbers for SFL}\Rui{explain what $k$ is for SFL alone.}}
  \label{table:fsws}
\end{table*}

@@

\subsection{Threats to validity}
%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.

@@

Program Slicing is an old technique with several applications in PL
and SE research~\cite{Weiser:1981:PS:800078.802557}. Slicing can be
implemented in different ways. Dynamic Slicing has found its main
application in fault
localization~\cite{Agrawal:1990:DPS:93542.93576}---in this application
context, failing tests exist. Research in this area has mainly focused
on slicing code
efficiently~\cite{Wang:2008:DSJ:1330017.1330021,Wang:2004:UCB:998675.999455}
and avoiding data and control omission
errors~\cite{Zhang:2007:TLE:1250734.1250782,Lin:2018:BDE:3238147.3238163}. Omission errors correspond to the
cases where tests fail because some part of the code was not executed
when it should. Dynamic fault localization techniques cannot hope to
soundly report bugs in those cases. The issue is that incorporating
static information to capture those cases can result in unacceptably
large slices, which defeats the purpose of reducing the fault search
space. It is worth noting that, conceptually, the \sfl{}+\ds{} combination
can be used with any form of dynamic slicing. We chose an
implementation of Critical
Slicing~\cite{DeMillo:1996:CSS:229000.226310} for its generality.

@@

Spectrum-based fault localization (\sfl{}) is amongst the most common statistical
fault localization technique that takes as input a test suite including at least
one failing test and reports on output a ranked list of components likely to be
in fault ~\cite{FLSurvey2016,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.

\subsection{Combination of \sfl{} and Slicing}
